The Chemistry Development Kit (CDK) v2.0: atom typing, depiction, molecular formulas, and substructure searching

### 2017-03-26 article.tex
Shorted the sentences (rev #2)

  Previous versions of the API represented stereochemistry in different ways, this hindered
  interconversion between and within file formats CDK \cdkversion{} standardizes
  upon a new core representation and procedures have been updated or added to
  enable duplicate checking, pattern matching, and interconversion.

@@

  Rendering is split up into several generation steps, previous versions split
  up bond from atom rendering, heteroatom symbols were simply drawn over lines
  representing bonds using a white rectangle to mask. A new \texttt{StandardGenerator}
  has been introduced that does bond and atom rendering at the same time, it incorporates
  many ideas described by Alex Clark~\cite{Clark10,Clark13}. The depictions generated are of much
  higher quality and suitable for publication.

>>>>

  Previous versions of the API represented stereochemistry in different ways. This hindered
  interconversion between and within file formats. CDK \cdkversion{} standardizes
  upon a new core representation and procedures have been updated or added to
  enable duplicate checking, pattern matching, and interconversion.

@@

  Rendering is split up into several generation steps: previous versions split
  up bond from atom rendering. Heteroatom symbols were simply drawn over lines
  representing bonds using a white rectangle to mask. A new \texttt{StandardGenerator}
  has been introduced that does bond and atom rendering at the same time. It incorporates
  many ideas described by Alex Clark~\cite{Clark10,Clark13}. The depictions generated are of much
  higher quality and suitable for publication.
